A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-09-18 uploaded_to_arXiv_16-09-18/Trick_J1331_Modelling_ARXIV.tex
Merging problems....

%============================================
\begin{table*}
\centering
\caption{Total $I$-band luminosity, stellar mass and mass-to-light ratio, calculated from the $I$-band AB magnitudes and stellar masses found for J1331's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work. The transformation from AB magnitudes to the Johnson-Cousins $I$-band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2). For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the WMAP5 cosmology by \citet{WMAP5cosm}. }
\begin{tabular}{cccccc}
\hline\hline
& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}\text{M}_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}\text{M}_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
\end{tabular}
\label{tab:previousresults}
\end{table*}
%============================================

@@

@@

%--------------------------------------------
\bibliographystyle{mnras}
\bibliography{literaturelist}
%--------------------------------------------

>>>>

@@

%============================================
\begin{table*}
\centering
\caption{Total $I$-band luminosity, stellar mass, and mass-to-light ratio, calculated from the $I$-band AB magnitudes and stellar masses found for J1331's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work. The transformation from AB magnitudes to the Johnson-Cousins $I$-band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2). For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the WMAP5 cosmology by \citet{WMAP5cosm}. }
\begin{tabular}{cccccc}
\hline\hline
& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}\text{M}_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}\text{M}_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
\end{tabular}
\label{tab:previousresults}
\end{table*}
%============================================

@@

%--------------------------------------------
\bibliography{literaturelist}{}
\bibliographystyle{mnras}
%--------------------------------------------
